workshop

### 2023-02-21 scripts/workshop/workshop.Rmd
update titles
try 3d model
another 3d plot

@@

@@

@@

@@

@@

>>>>

# Incidence

@@

# Prevalence

@@

# Abundance

@@

# Histograms

@@

# Effect Sizes

@@

```{r}
library(plotly)
```

```{r}
plot_ly(data = effect_summ, x=effect_summ$temp_over, y=effect_summ$size_over, z=effect_summ$cc_over, 
        type="scatter3d", mode="markers", color=as.factor(effect_summ$WetAltID))

plot_ly(data = effect_summ, x=effect_summ$temp_sum, y=effect_summ$size_sum, z=effect_summ$cc_sum, 
        type="scatter3d", mode="markers", color=as.factor(effect_summ$WetAltID))
```
